### 2019-10-18 source/cadabra/sqrt-detg.tex
Updated Makefile to *not* make sqrt-detg
The sqrt-detg code requires pylatex.sh and friends which are not included in this repo. (see https://github.com/leo-brewin/hybrid-latex). The sqrt-detg results are not required by any code here. It's output was hand coded in detg.tex.

Also, the cdbpreproc.py was updated (copied from hybrid-latex repo.).
See https://github.com/leo-brewin/hybrid-latex/commit/199d8e817b54ca515c1221aee749990829b69538

   ans = sqrt(1+a*eps**2+b*eps**3+c*eps**4+d*eps**5)   # py(ans.001,ans)
   ans = ans.series(eps, 0, 6)                         # py(ans.002,ans)
   ans = simplify(ans)                                 # py(ans.003,ans)

@@

   ans = log(1+a*eps**2+b*eps**3+c*eps**4+d*eps**5)    # py(ans.101,ans)
   ans = ans.series(eps, 0, 6)                         # py(ans.102,ans)
   ans = simplify(ans)                                 # py(ans.103,ans)

>>>>

   ans = sqrt(1+a*eps**2+b*eps**3+c*eps**4+d*eps**5)   # py (ans.001,ans)
   ans = ans.series(eps, 0, 6)                         # py (ans.002,ans)
   ans = simplify(ans)                                 # py (ans.003,ans)

@@

   ans = log(1+a*eps**2+b*eps**3+c*eps**4+d*eps**5)    # py (ans.101,ans)
   ans = ans.series(eps, 0, 6)                         # py (ans.102,ans)
   ans = simplify(ans)                                 # py (ans.103,ans)
